Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
Predicate system for presheaf category.

Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over $\Set$,
$\cat{C}$ a category and $F: \cat{C}^\op \to \Set$ a presheaf. Define a predicate on $F$ to be a family of
predicates $P_X \in \Pred_\mathcal{S}(F(X))$ for every object $X$ in $\cat{C}$ such that $P_Y \sqsubseteq
\reindex{P_X}{F(f)}$ for every $f: X \to Y$ in $\cat{C}$. Define $\mathcal{S}^{\cat{C}}$ to be the predicate
system which assigns to every presheaf $F$ the poset $(\Pred(F), \sqleq)$ of predicates on $F$ ordered
pointwise, and where $\top, \meet, \join, \residual$ and $\forall$ are all computed pointwise.

>>>>

Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over $\Set$,
$\cat{C}$ a category and $F: \cat{C}^\op \to \Set$ a presheaf. Define a predicate on $F$ to be a family of
predicates $P_X \in \Pred_\mathcal{S}(F(X))$ for every object $X$ in $\cat{C}$ such that $P_Y \sqsubseteq
\reindex{P_X}{F(f)}$ for every $f: X \to Y$ in $\cat{C}$. Now define $\mathcal{S}^{\cat{C}}$ to be the
predicate system which assigns to every presheaf $F$ the poset $(\Pred(F), \sqleq)$ of predicates on $F$
ordered pointwise, and where $\top, \meet, \join, \residual$ and $\forall$ are all computed pointwise.
